R Markdown for Reproducible Research

### 2019-01-06 paper.Rmd
add a few todo items
add a few tips and tricks

- Code chunk options
- Knit options
- URLs and internal links
- RStudio documentation, etc

@@

### TODO
- Link for YAML syntax
- Link for YAML header docs
- Resource on R as an interface language

>>>>

- Code chunk options
- Knit options
- URLs and internal links
- Table of Contents
- Table Output
- RStudio documentation, etc

@@

### TODO
- Link for YAML syntax
- Link for YAML header docs
- Resource on R as an interface language
- link to figures / images
- start managing references better...
